An \glsdesc{acr:oqe} \gls{seismicsourceinputmodel} contains a list of sources
belonging to a finite set of possible typologies. Each source type is defined
by a set of parameters - called source data - which are used to specify the
source geometry and the properties of seismicity occurrence.

Currently the \glsdesc{acr:oqe} supports the following source types:

\begin{itemize}

    \item Sources for modelling distributed seismicity:

    \begin{itemize}

        \item \Gls{pointsource} - The elemental source type used to model
        distributed seismicity. Grid and area sources (described below) are
        different containers of point sources.

        \item \Gls{areasource} - So far, the most frequently adopted source
        type in national and regional PSHA models.

        \item \Gls{gridsource} - A replacement for area sources admitting
        spatially variable seismicity occurrence properties.

    \end{itemize}

    \item Fault sources with floating ruptures:

    \begin{itemize}

        \item \Gls{simplefaultsource} - The simplest fault model in the
        \glsdesc{acr:oqe}. This source is habitually used to describe shallow
        seismogenic faults.

        \item \Gls{complexfaultsource} - Often used to model subduction
        interface sources with a complex geometry.

    \end{itemize}

    \item Fault sources with ruptures always covering the entire fault
    \surface:

    \begin{itemize}

        \item \Gls{charfaultsource} - A typology of source where ruptures
        always fill the entire fault surface.

    \end{itemize}

\end{itemize}

The \glsdesc{acr:oqe} contains some basic assumptions for the definition of
these source typologies:

\begin{itemize}

    \item In the case of area and fault sources, the seismicity is
    homogeneously distributed over the source;

    \item Seismicity temporal occurrence follows a Poissonian model.

\end{itemize}



\subsection{Source typologies for modelling distributed seismicity}
\input{oqum/hazard/00a_sources_distributed_seismicity}

\subsection{Fault sources with floating ruptures}
\input{oqum/hazard/00a_sources_floating_ruptures}

\subsection{Fault sources without floating ruptures}
\input{oqum/hazard/00a_sources_nonfloating_ruptures}
