\label{sec:gmpes_list}
We provide below a list of the ground motion prediction equations 
implemented in the \gls{acr:hazlib}. All the implemented \gls{acr:gmpe}
use moment magnitude as the reference magnitude.
%
\section{Ground motion prediction equations for shallow earthquakes 
    in active tectonic regions}
\begin{itemize} 
    \item \cite{abrahamson2008} - A ground motion prediction equation 
        developed in the context of the NGA West project \hfill \\
        (\href{http://peer.berkeley.edu/ngawest/}{http://peer.berkeley.edu/ngawest})
    \item \cite{akkar2010} - A ground motion prediction equation 
        developed using mostly data from Europe and the Middle East. The dataset 
        used to derive these equations contains events with moment 
        magnitude between 5 and 7.6 and distances up to 100 km.
    \item \cite{akkar2010a} - A ground motion prediction equation for shallow
        earthquakes in active tectonic regions developed using data from the 
        Turkish strong-motion database. Equations are valid for a distance 
        %(\gls{acr:rjb}) range of 0–200 km and are derived for moment magnitudes 
        range of 0–200 km and are derived for moment magnitudes 
        between 5 and 7.6.
    \item \cite{boore2008} - A ground motion prediction equation 
        for shallow earthquakes in active tectonic regions developed in 
        the context of the NGA West project \hfill \\
        (\href{http://peer.berkeley.edu/ngawest/}
        {http://peer.berkeley.edu/ngawest/})
    \item \cite{cauzzi2008} - A ground motion prediction equation 
        developed in using mostly japanese strong ground motion recordings.
    \item \cite{chiou2008} - A ground motion prediction equation 
        for shallow earthquakes in active tectonic regions developed in 
        the context of the NGA West \hfill \\
        (\href{http://peer.berkeley.edu/ngawest/}
        {http://peer.berkeley.edu/ngawest/})
    \item \cite{sadigh1997} - A \gls{acr:gmpe} based on strong motion data 
        from California. 
    \item \cite{zhao2006} - A ground motion prediction equation 
        developed using mostly japanese strong ground motion 
        recordings. 
\end{itemize}
%
\section{Ground motion prediction equations for subduction sources}
\begin{itemize}
    \item \cite{atkinson2003} - A ground motion prediction equation for 
        subduction interface and in-slab events obtained using a global 
        dataset of subduction earthquakes with moment magnitude between 
        5.0 and 8.3.
    \item \cite{lin2008} - A \gls{acr:gmpe} created using strong motion
        data included in the the Taiwanese database.
    \item \cite{youngs1997} - One of the most well known ground motion 
        prediction equations for subduction earthquakes. Published in 1997,
        is still currently used for the calculation of the ground motion 
        in subduction tectonic environments. This GMPE covers events of 
        moment magnitude greater than 5 occurred at a distance between 5
        and 500 km. The source-site distance metric is the \gls{acr:rrup}.
    \item \cite{zhao2006} - A ground motion prediction equation 
        developed using mostly japanese strong ground motion 
        recordings.
\end{itemize}
%
\section{Ground motion prediction equations for stable continental regions}
\begin{itemize}
    \item \cite{atkinson2006} - A ground motion prediction equation for 
    Stable Continental regions.
    \item \cite{campbell2003}
    \item \cite{toro2002}
\end{itemize}
%
\section{Ground motion prediction equations for volcanic areas}
\begin{itemize}
    \item \cite{faccioli2010}
\end{itemize}
