\index{OpenQuake-engine!risk}

The seismic risk results are being calculated using the OpenQuake risk library
(oq-risklib), an open-source suite of tools for seismic risk assessment and
loss estimation. This library is written in the Python programming language
and available in the form of a ``developers'' release, that can be executed
through a command line interface. The code of the library can be found on a
public repository at GitHub at the following address
\href{http://github.com/gem/oq-risklib}{http://github.com/gem/oq-risklib}.

The risk component of the OpenQuake-engine can compute both scenario-based and
probabilistic seismic damage and risk using various approaches. The following
types of analysis are currently supported:

\begin{itemize}

    \item \textit{Scenario Damage Assessment}, allowing the calculation of
	damage distribution statistics for a portfolio of buildings from a single
	earthquake rupture scenario taking into account aleatory and epistemic
	ground-motion variability.

	\item \textit{Scenario Risk Assessment}, for the calculation of individual 
	asset and portfolio loss statistics due to a single earthquake 
	rupture scenario taking into account aleatory and epistemic ground-motion 
	variability. Correlation in the vulnerability of different assets of the 
	same typology can also be taken into consideration.

	\item \textit{Classical Probabilistic Seismic Damage Analysis}, for 
	calculation of damage state probabilities over a specified time period,  
	and probabilistic collapse maps, starting from the hazard curves 
	computed following the classical integration procedure (\cite{cornell1968}, 
	\citet{mcguire1976}) as formulated by \cite{field2003}.

    \item \textit{Classical Probabilistic Seismic Risk Analysis}, allowing
	calculation of loss curves and loss maps, starting from the hazard curves 
	computed following the classical integration procedure (\cite{cornell1968}, 
	\citet{mcguire1976}) as formulated by \cite{field2003}.

	\item \textit{Event-Based Probabilistic Seismic Risk Analysis}, 
	allowing calculation of event-loss tables starting from stochastic event sets.
	Other results such as loss-exceedance curves, probabilistic loss maps, 
	average annual losses, and insured loss statistics can be obtained by post-
	processing the event-loss tables.

	\item \textit{Retrofit Benefit-Cost Ratio Analysis}, which is useful in 
	estimating the net-present value of the potential benefits of performing  
	retrofitting for a portfolio of assets (in terms of decreased losses in 
	seismic events), measured relative to the upfront cost of retrofitting.

\end{itemize}

Each calculation workflow has a modular structure, so that intermediate
results can be exported and analyzed. Moreover, each calculator can be
extended independently of the others so that additional calculation options
and methodologies can be easily introduced, without affecting the overall
calculation workflow.

The following sections describe the basic inputs required for a risk
calculation, including exposure models, fragility models, consequence models,
and vulnerability models. The final section of this chapter describes each of
the above workflows in detail.

For further information regarding the theoretical background of the
methodologies used for each calculator, users are referred to the OpenQuake-
engine Book (Risk).


\section{Exposure models}
\label{sec:exposure}
\input{oqum/risk/00a_exposure}

\section{Fragility models}
\label{sec:fragility}
\input{oqum/risk/00b_fragility}

\section{Consequence models}
\label{sec:consequence}
\input{oqum/risk/00c_consequence}

\section{Vulnerability models}
\label{sec:vulnerability}
\input{oqum/risk/00d_vulnerability}

\section{Calculation workflows}
\label{sec:risk_workflows}
\input{oqum/risk/00e_risk_workflows}