This Chapter summarises the structure of the information necessary to define
the different input data to be used with the OpenQuake-engine risk
calculators. Input data for scenario-based and probabilistic seismic damage
and risk analysis using OpenQuake-engine are organised into:

\begin{itemize}

  \item An exposure model file in the NRML format, as described in 
    Section~\ref{sec:exposure}.

  \item A file describing the \gls{vulnerability model}
    (Section~\ref{sec:vulnerability}) for loss calculations, or a 
  	file describing the \gls{fragility model} (Section~\ref{sec:fragility})
    for damage calculations. Optionally, a file describing the
    \gls{consequence model} (Section~\ref{sec:consequence}) can also be
  	provided in order to calculate losses from the estimated damage
  	distributions.

  \item A general calculation configuration file.

  \item Hazard inputs. These include hazard curves for the classical
    probabilistic damage and risk calculators, ground motion fields for the
    scenario damage and risk calculators, or stochastic event sets for the
    probabilistic event based calculators. As of OpenQuake-engine v1.6, in
    general, there are five different ways in which hazard calculation
    parameters or results can be provided to the OpenQuake-engine in order to
    run the subsequent risk calculations:

    \begin{itemize}

      \item Use a single configuration file for running the hazard and risk
      calculations sequentially

      \item Use separate configuration files for running the hazard and risk
      calculations sequentially

      \item Use a configuration file for the risk calculation along with all
      hazard outputs from a previously completed, compatible
      OpenQuake-engine hazard calculation

      \item Use a configuration file for the risk calculation along with a
      specific hazard output from a previously completed, compatible
      OpenQuake-engine hazard calculation

      \item Use a configuration file for the risk calculation along with
      hazard input files in the OpenQuake NRML format

    \end{itemize}

\end{itemize}

The file formats for exposure, fragility, consequence, and vulnerability
models have been described earlier in Chapter~\ref{chap:riskintro}. The
configuration file is the primary file that provides the OpenQuake-engine
information regarding both the definition of the input models (e.g. exposure,
site parameters, fragility, consequence, or vulnerability models) as well as
the parameters governing the risk calculation.

Information regarding the configuration file for running hazard calculations
using OpenQuake-engine can be found in
Section~\ref{sec:hazard_configuration_file}. Some initial parameters of the
configuration file common to all of the risk calculators are presented below.
The remaining parameters that are specific to each risk calculator are
discussed in subsequent sections.

\inputminted[firstline=1,firstnumber=1,fontsize=\footnotesize,frame=single,linenos,bgcolor=lightgray]{ini}{oqum/risk/Verbatim/config_example.ini}\\

\begin{itemize}

  \item \Verb+description+: a parameter that can be used to include some
  information about the type of calculations that are going to be performed.

  \item \Verb+calculation_mode+: this parameter specifies the type of
  calculation to be run. Valid options for the \Verb+calculation_mode+ for
  the risk calculators are: \Verb+scenario_damage+, \Verb+scenario_risk+,
  \Verb+classical_damage+, \Verb+classical_risk+, \Verb+event_based_risk+,
  and \Verb+classical_bcr+.

  \item \Verb+exposure_file+: this parameter is used to specify the path to
  the \gls{exposure model} file.

\end{itemize}

Depending on the type of risk calculation, other parameters besides the
aforementioned ones may need to be provided. We illustrate in the following
sections different examples of the configuration file for the different risk
calculators.


\section{Scenario Damage Calculator}
\label{sec:config_scenario_damage}
\input{oqum/risk/02_config_scenario_damage}

\section{Scenario Risk Calculator}
\label{sec:config_scenario_risk}
\input{oqum/risk/02_config_scenario_risk}

\section{Classical Probabilistic Seismic Damage Calculator}
\label{sec:config_classical_damage}
\input{oqum/risk/02_config_classical_damage}

\section{Classical Probabilistic Seismic Risk Calculator}
\label{sec:config_classical_risk}
\input{oqum/risk/02_config_classical_risk}

\section{Event-Based Probabilistic Seismic Risk Calculator}
\label{sec:config_event_based_risk}
\input{oqum/risk/02_config_event_based_risk}

\section{Retrofit Benefit-Cost Ratio Calculator}
\label{sec:config_benefit_cost}
\input{oqum/risk/02_config_benefit_cost}

\section{Running the Risk Calculators}
\label{sec:running_risk}
\input{oqum/risk/02b_running}

\cleardoublepage